CVS Installation und Konfiguration

### 2014-10-28 CM-Scripts/studentuserlist.tex
list refreshed

\rowcolor{yellow}\cellcolor{red}diplomand7 &rsteinbrueck&René Steinbrück&rene.steinbrueck@fernuni-hagen.de&                     &16.06.14     &\\

@@

\cellcolor{green}diplomand21\\

@@

\cellcolor{green}diplomand30\\

>>>>

\rowcolor{yellow}\cellcolor{red}diplomand7 &rsteinbrueck&René Steinbrück&rene.steinbrueck@fernuni-hagen.de&Algebras/LineFunction&16.06.14     &\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand21&seiersbrock&Simon Eiersbrock&mail@simoneiersbrock.de&students/Eiersbrock            &21.10.14&\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand30&chengwang&Cheng Wang      &cheng.wang.t@gmail.com&Algebras/FText                    &22.09.14&\\
